\section*{Revision History}
\label{sec:revision_history}

\begin{longtable}{|c|p{.65\columnwidth}|c|}
% \caption{Explanation of Listing~\ref{lst:muon_conditions_vhd}}\\
\hline
Doc Rev & Description of Change & Revision Date\\
\hline
\hline
\endhead
5.2 & Bug fixed in definition of calo eta ranges (\ref{sec:gtl:calorimeter_data}). & 2021/11/30\\
5.1 & Updated data structure for jets with DISP bit (\ref{sec:gtl:gct_optical_interfaces}). & 2021/11/17\\
5.0 & Inserted "Calculation of look-up-tables (LUTs) for correlation cuts" (\ref{sec:gtl:calc_luts_corr_cuts}). & 2021/11/10\\
4.9 & Updated (and renamed) description of "Invariant mass over delta R calculation" (see \ref{sec:gtl:inv_mass_div_dr_calculation}). & 2021/09/14\\
4.8 & Fixed typo in section "Invariant mass calculation for three objects" \ref{sec:gtl:inv_mass_3_obj_calculation}. & 2020/12/03\\
4.7 & Inserted links to VHDL modules. & 2020/09/18\\
4.6 & Updated text in section "Correlation conditions" \ref{sec:gtl:correlation_conditions}. Description is for v1.10.0 of Global Trigger Logic. & 2020/09/17\\
4.5 & Inserted description of "Invariant mass divided by delta R calculation" (see \ref{sec:gtl:inv_mass_div_dr_calculation}). & 2020/09/10\\
4.4 & Fixed typo (unconstrained pt). & 2020/09/09\\
4.3 & Inserted text for new muon structure in sections \ref{sec:gtl:gmt_optical_interfaces} and \ref{sec:gtl:muon_data}. & 2020/08/04\\
4.2 & Additional text in section calo calo overlap remover condition module. & 2020/05/25\\
4.1 & Updated glossary. & 2020/04/21\\
4.0 & Removed listings (not usefull for emulator designers). & 2020/04/17\\
3.9 & Inserted text in section Calorimeter Overlap Remover conditions and Calo Calo Overlap Remover Correlation conditions. & 2020/04/16\\
3.8 & Updated text in sections Calorimeter conditions, Muon conditions and Correlation conditions for changes which have been done for GTL VHDL version 1.8.0 (module names without version number, "five eta cuts"). & 2019/08/13\\
3.7 & Inserted "Asymmetry" and "Centrality" of "Energy sums" (GTL VHDL version 1.6.0). & 2018/08/13\\
3.6 & Updated text in section "Global Trigger Logic" (\ref{sec:gtl:global_trigger_logic}) according to firmware version v1.5.0 of gtl\_module.vhd & 2018/02/21\\
3.5 & Inserted text for "Minimum bias trigger conditions" (\ref{sec:gtl:min_bias_conditions}) and "Towercount condition" (\ref{sec:gtl:towercount_cond}).
Updated glossary. & 2016/11/28\\
3.4 & Updated text in section "Muon Muon Correlation condition module". & 2016/01/15\\
3.3 & Removed "Double objects requirements condition with spatial correlation", because not used anymore in the future, replaced by Correlation conditions. & 2016/01/08\\
3.2 & Minor changes in text and updated Figure \ref{fig:gtl:gtl_pipeline}. & 2016/01/08\\
3.1 & Changed colour in Figure \ref{fig:gtl:phi_windows_comparator} and updated text for correlation conditions (see section~\ref{sec:gtl:correlation_conditions}. & 2016/01/07\\
3.0 & Updated Figures \ref{fig:gtl:gtl_pipeline} and text calo calo correlation condition module. & 2015/12/21\\
2.9 & Inserted drawing of VHDL structure of cuts for correlation conditions (see Figure~\ref{fig:gtl:scheme_vhdl_cuts_correllation_condition}). & 2015/11/18\\
2.8 & Updated muon $\eta$ ranges (Table~\ref{tab:gtl:muon_eta_scale}) and inserted correlation conditions.
Created scheme for conversion of calorimeter $\eta$ and $\varphi$ to muon scale for calo muon correlation conditions. & 2015/11/17\\
2.7 & Added text in sections Calo comparator module and Muon comparator module. & 2015/10/08\\
2.6 & Remaned section "Calorimeter conditions module - version 2" to "Calorimeter conditions module - version 3", section "Muon conditions module" to "Muon conditions module - version 2" and section "Muon comparators module" to "Muon comparators module - version 2". & 2015/10/02\\
2.5 & Updated text and tables of $\eta$ ranges for Calorimeter objects (see \ref{sec:gtl:calorimeter_data}). & 2015/09/22\\
2.4 & Corrected calculation of muon $\eta$ step width (see \ref{sec:gtl:muon_data}). & 2015/09/10\\
2.3 & Edited text in Table \ref{tab:gtl:muon_lut_qual}. & 2015/08/28\\
2.2 & Updated definition of $\eta$ ranges for Calorimeter objects and Muon objects (\ref{sec:gtl:calorimeter_data} and \ref{sec:gtl:muon_data}). & 2015/08/20\\
2.1 & Added section Calo Muon Correlation condition. & 2015/08/19\\
2.0 & Added section "Correlation conditions" (\ref{sec:gtl:correlation_conditions}). & 2015/06/19\\
1.9 & Added tables for calorimeter isolation-bits and for muon quality- and isolation-bits definition (\ref{tab:gtl:eg_tau_iso_bits}, \ref{tab:gtl:muon_quality_bits} and \ref{tab:gtl:muon_iso_bits}).
Edited section glossary (\ref{sec:glossary}) and acronyms. & 2015/05/07\\
1.8 & Added text for "Energy sum conditions" (\ref{sec:gtl:esums_conditions}) and updated chapters for "Calorimeter conditions" for version 2. Inserted isolation bits for \egamma and tau objects
(\ref{sec:gtl:calorimeter_data}). & 2015/05/06\\
1.7 & Minor changes in sections "Muon data" (\ref{sec:gtl:muon_data}). & 2014/11/06\\
1.6 & Minor changes in sections "Calorimeter conditions definition" and "Muon conditions definition". & 2014/07/01\\
1.5 & Minor changes & 2014/06/12\\
1.4 & Fixed bug in Figure \ref{fig:gtl:phi_windows_comparator} & 2014/04/30\\
1.3 & Added section "Muon conditions". & 2014/04/22\\
1.2 & Changed Figure \ref{fig:gtl:phi_windows_comparator} and minor changes in text for anti-clockwise behaviour in $\varphi$ & 2014/04/04\\
1.1 & Changed text in section Calo conditions definition. & 2014/02/11\\
1.0 & Document created. Description of Calorimeter conditions. & 2013/10/15\\
\hline
%\label{tab:gtl:explanation_muon_conditions_vhd}
\end{longtable}

\clearpage{}
